---
title: "Open Science & Open Source Ecosystem Map"
format:
  html:
    toc: true
    theme: cosmo
    embed-resources: true
    smooth-scroll: true
lang: en
---

This page visualizes key organizations, platforms, and initiatives that make up the open science and open source ecosystem. Categories span community groups, infrastructure, funding, publishing, and beyond. Click on a category to jump to its section.

_If you know an organization that should be featured here, [add it to the spreadsheet](https://docs.google.com/spreadsheets/d/1zJCC9ZTXxz4J8aUY_FdyI3b0x34zzwi_p_KUymIOyxw/edit?usp=sharing) and and rebuild this report!_

Tables are generated automatically from the [community spreadsheet](https://docs.google.com/spreadsheets/d/1zJCC9ZTXxz4J8aUY_FdyI3b0x34zzwi_p_KUymIOyxw/edit?usp=sharing).

```{r message=FALSE, warning=FALSE}
#| include: false
library(readr)
library(dplyr)
library(knitr)

# This is the CSV export URL for the Google Sheet (export as CSV)
sheet_csv <- "https://docs.google.com/spreadsheets/d/1zJCC9ZTXxz4J8aUY_FdyI3b0x34zzwi_p_KUymIOyxw/export?format=csv"

orgs <- read_csv(sheet_csv, show_col_types = FALSE)

# Make sure names and links are clean
orgs <- orgs %>%
  mutate(
    Website = ifelse(!grepl("^https?://", Website), paste0("https://", Website), Website),
    Category = trimws(Category),
    Organization = trimws(Organization),
    Description = trimws(Description)
  )
```


```{r}
#| include: false
categories <- unique(orgs$Category)
categories
```

---

## Categories

- [Community & Networking](#community--networking)
- [Funding & Grants](#funding--grants)
- [Infrastructure & Platforms](#infrastructure--platforms)
- [Training & Education](#training--education)
- [Publishing & Peer Review](#publishing--peer-review)
- [Standards & Best Practices](#standards--best-practices)
- [Advocacy & Policy](#advocacy--policy)
- [Collaboration Tools](#collaboration-tools)
- [Others Categories](#other-categories)

---

## Community & Networking{#community--networking}

```{r}
#| echo: false
community_tbl <- orgs %>%
  filter(tolower(Category) == "community & networking") %>%
  select(Organization, Description, Website)

kable(community_tbl, escape = FALSE, format = "html", col.names = c("Organization", "Description", "Website"))
```

---

## Funding & Grants{#funding--grants}

```{r}
#| echo: false
funding_tbl <- orgs %>%
  filter(tolower(Category) == "funding & grants") %>%
  select(Organization, Description, Website)

kable(funding_tbl, escape = FALSE, format = "html", col.names = c("Organization", "Description", "Website"))
```

---

## Infrastructure & Platforms{#infrastructure--platforms}

```{r}
#| echo: false
infra_tbl <- orgs %>%
  filter(tolower(Category) == "infrastructure & platforms") %>%
  select(Organization, Description, Website)

kable(infra_tbl, escape = FALSE, format = "html", col.names = c("Organization", "Description", "Website"))
```

---

## Training & Education{#training--education}

```{r}
#| echo: false
training_tbl <- orgs %>%
  filter(tolower(Category) == "training & education") %>%
  select(Organization, Description, Website)

kable(training_tbl, escape = FALSE, format = "html", col.names = c("Organization", "Description", "Website"))
```

---

## Publishing & Peer Review{#publishing--peer-review}

```{r}
#| echo: false
publishing_tbl <- orgs %>%
  filter(tolower(Category) == "publishing & peer review") %>%
  select(Organization, Description, Website)

kable(publishing_tbl, escape = FALSE, format = "html", col.names = c("Organization", "Description", "Website"))
```

---

## Standards & Best Practices{#standards--best-practices}

```{r}
#| echo: false
standards_tbl <- orgs %>%
  filter(tolower(Category) == "standards & best practices") %>%
  select(Organization, Description, Website)

kable(standards_tbl, escape = FALSE, format = "html", col.names = c("Organization", "Description", "Website"))
```

---

## Advocacy & Policy{#advocacy--policy}

```{r}
#| echo: false
advocacy_tbl <- orgs %>%
  filter(tolower(Category) == "advocacy & policy") %>%
  select(Organization, Description, Website)

kable(advocacy_tbl, escape = FALSE, format = "html", col.names = c("Organization", "Description", "Website"))
```

---

## Collaboration Tools{#collaboration-tools}

```{r}
#| echo: false
collab_tbl <- orgs %>%
  filter(tolower(Category) == "collaboration tools") %>%
  select(Organization, Description, Website)

kable(collab_tbl, escape = FALSE, format = "html", col.names = c("Organization", "Description", "Website"))
```

---

## All Other Categories{#other-categories}

```{r}
#| echo: false
other_tbl <- orgs %>%
  filter(!(tolower(Category) %in%
     c("community & networking",
       "funding & grants",
       "infrastructure & platforms",
       "training & education",
       "publishing & peer review",
       "standards & best practices",
       "advocacy & policy",
       "collaboration tools"))) %>%
  select(Category, Organization, Description, Website)

if (nrow(other_tbl) > 0) {
  kable(other_tbl, escape = FALSE, format = "html", col.names = c("Category", "Organization", "Description", "Website"))
} else {
  cat("No additional categories.")
}
```

---

## Add or Update Organizations

You can add or request corrections to the list by editing the [Google Sheet](https://docs.google.com/spreadsheets/d/1zJCC9ZTXxz4J8aUY_FdyI3b0x34zzwi_p_KUymIOyxw/edit?usp=sharing).  
This report will update automatically on rebuild!

---

## About

This map is curated by the open science community.  
First version by [@yabellini](https://github.com/yabellini). 
Updated by ORCA CAP Projects 2025

